GVN-Hoist: Hoisting Computations from Branches

### 2016-08-08 hoist.tex
restructure the overview of algo

\section{Code hoisting}

\subsection{Overview}

@@

For legality we have to check that the side-effects of call does not intersect
any side-effect between the instruciton to be hoisted and its hoisting point.

@@

\subsection{Algorithm}
A good full page.

\subsubsection{Hoisting bottom up with optimistic approach}
Optimistic means collect the set of all potential redundancies and
then discard the bad ones.

>>>>

@@

\section{Code hoisting}
Similar to most compiler optimization passes the code-hoisting pass can also be
divided into the following five steps:

\subsection{Finding the candidates}
Finding if a set of instructions perform identical computations. Since this code
hoisting is based on GVN, all we need to do is to compare the value number of
computations.

\subsection{Checking for legality}
Finding a hoisting point i.e. a common dominator of the set of instructions. If
such a dominator is found then checking if all the use-operands of the set of
instructions are available or not. In some cases if the operands are not
available, it is possible to reinstantiate (remateralize) the use-operands, thus
making the passing the legality check. Checking that the side-effects of the
computations does not intersect with any side-effect between the instructions to
be hoisted and their hoisting point. For memory operations like loads, stores,
calls etc., it is also required to check that all the paths from the hoisting
point to the end of the function should have the exact memory operation
available, in order to guarantee correctness.

@@

\subsection{Checking for profitability}
Establishing a set of cost models tune for performance. Like decreasing code
size, minimizing spills etc.

\subsection{Making the transformation}
Putting a copy of the computation at the hoisting point and removing all the
computations made redundant by the new copy.

\subsection{Verification}
Performing a set of checks (e.g., consistency of use-defs and SSA semantics) to
establish that program invariants are maintained.

\subsection{Hoisting bottom up with optimistic approach}
Optimistic means collect the set of all potential redundancies and
then discard the bad ones.
